Packaging research artifacts with RO-Crate

### 2021-05-04 latex/ro-crate.tex
use ro-crate.bib
markdown settings
fixing more DOIs and markdown
using iosevka light

@@

\DeclareGraphicsExtensions{.png,.pdf}
\graphicspath{../content/images/}
\usepackage[smartEllipses,tableCaptions,pipeTables,fencedCode,footnotes,underscores,hybrid]{markdown}
\def\markdownOptionOutputDir{../output}

@@

\setmathfont{STIX2Math}[
Extension={.otf},
Path=./STIX2fonts/,
Scale=1]
\setmainfont{STIX2Text}[
Extension={.otf},
Path=./STIX2fonts/,
UprightFont={*-Regular},
BoldFont={*-Bold},
ItalicFont={*-Italic},
BoldItalicFont={*-BoldItalic}]

@@

%\section{}\label{s1}

%\subsection{}\label{s1.1}

\markdownInput{../content/10.background.md}
\markdownInput{../content/20.rocrate.md}
\markdownInput{../content/21.conceptual.md}
\markdownInput{../content/22.implementation.md}
\markdownInput{../content/23.community.md}
\markdownInput{../content/30.tooling.md}
\markdownInput{../content/40.inuse.md}
\markdownInput{../content/50.relatedwork.md}
\markdownInput{../content/60.conclusion.md}
\markdownInput{../content/80.formal-definition.md}

@@

\nocite{*} 
% if your bibliography is in bibtex format, use those commands:
\bibliographystyle{ios1}           % Style BST file.
\bibliography{bibliography}        % Bibliography file (usually '*.bib')

>>>>

%\usepackage[backend=biber]{biblatex}
%\addbibresource{ro-crate.bib}

@@

\DeclareGraphicsExtensions{.png,.pdf}
\graphicspath{../content/images/}
\usepackage[citations,fencedCode,footnotes,hybrid,pipeTables,smartEllipses,tableCaptions,underscores]{markdown}
\def\markdownOptionOutputDir{../output}

@@

% Welcome to the 2000s with UNICODE fonts!
% Adapted from
% https://www.overleaf.com/learn/latex/Articles%2FOpenType-based_math_typesetting:_An_introduction_to_the_STIX2_OpenType_fonts
\setmathfont{STIX2Math}[
Extension={.otf},
Path=./STIX2fonts/,
Scale=1]
\setmainfont{STIX2Text}[
Extension={.otf},
Path=./STIX2fonts/,
UprightFont={*-Regular},
BoldFont={*-Bold},
ItalicFont={*-Italic},
BoldItalicFont={*-BoldItalic}]
% https://typeof.net/Iosevka/ mono font has 
% all; the logic symbols we need
\setmonofont{iosevka-slab}[
Extension={.otf},
Path=./ttf-iosevka-slab-6.1.3/,
Scale=MatchLowercase,
UprightFont={*-light},
ItalicFont={*-lightitalic}
]

@@

% Every *.md file in content in order, except 00, 90
\markdownInput{../content/10.background.md}
\markdownInput{../content/20.rocrate.md}
\markdownInput{../content/21.conceptual.md}
\markdownInput{../content/22.implementation.md}
\markdownInput{../content/23.community.md}
\markdownInput{../content/30.tooling.md}
\markdownInput{../content/40.inuse.md}
\markdownInput{../content/50.relatedwork.md}
\markdownInput{../content/60.conclusion.md}
\markdownInput{../content/80.formal-definition.md}
% TODO: Recode formal 
%\input{../content/80.formal-definition.tex}

@@

\nocite{*} 
% if your bibliography is in bibtex format, use those commands:
\bibliographystyle{ios1}           % Style BST file.
\bibliography{ro-crate}        % Bibliography file (usually '*.bib')
